---
title: "My first App_Developing data products"
author: "AM"
date: "2022-12-09"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## 1. Introduction

For the project I used Iris dataset. Shiny application was used to check the iris data attribude by Sepal.length, Sepal.Width, Petal.length, Petal.Width using histogram.

The dataset consists of 50 samples of 3 different species of iris.

In the presentation you will find ui.R file (information about slider bar) and server.R (information how to build the histogram).

## 2. Data exploration

```{r, echo = TRUE}
head(iris)
dim(iris)
```

## 3. Slide with ui.R code

```{r, echo = TRUE}
library(shiny)

# Define ui for Iris data that draws a histogram
shinyUI <- fluidPage(
  titlePanel("Iris Data Explorer"),
  
  # Sidebar with radio buttons for attribute option and a slider input for bins range 
  sidebarLayout(
    sidebarPanel(
      helpText("Select the attribute to know the variation of each measurement "),
      
      radioButtons("option", "Choose Iris attribute:", list("Sepal.Length"='a', "Sepal.Width"='b', "Petal.Length"='c', "Petal.Width"='d')),
      sliderInput("bins",
                  "Slide me to check the histogram of each attribute",
                  min = 1,
                  max = 50,
                  value = 30)
    ),
    
    # Visualization of Iris Dataset through Histogram
    mainPanel(
      mainPanel(plotOutput("distPlot"))
    )
  )
)
```

## 4. Slide with server.R code

```{r, echo = TRUE}
server <- function(input, output) {
    
    output$distPlot <- renderPlot({
        if(input$option=='a'){       
            i<-1     }     
        if(input$option=='b'){       
            i<-2     }     
        if(input$option=='c'){       
            i<-3     }     
        if(input$option=='d'){       
            i<-4     }
        
        # generate bins based on input$bins from ui.R
        x    <- iris[, i] 
        bins <- seq(min(x), max(x), length.out = input$bins + 1)
        
        # draw the histogram with the specified bins range
        hist(x, main = "Histogram of Iris Dataset", xlab = "Iris Attribute", ylab = "Frequency", breaks = bins, col = 'blue', border = 'white')
    })
}
```

## 5. Additional resources

1. Github link to ur.R and server.R files

https://github.com/AlenaMare/Shiny_project

2. Shinpy app

https://alenacize.shinyapps.io/alenamare/